\huge {\bold Parallel Algorithms}

### 2024-10-12 Papers/Parallel Aalgorithms/Booklet/PA.tex
Commit
docs(PA && LSSA): Complete Static Interconnection Networks
- add graphs shema to static interconnection networks
- update LSSA introduction

                        \begin{forest}
                            for tree={rounded corners,
                            draw,
                            text centered,
                            anchor=north,
                            grow=east,
                            anchor=west,
                            parent anchor=east,
                            child anchor=west,
                            l sep=1cm,
                            s sep=0.2cm,
                            tier/.wrap pgfmath arg={level#1}{level()}
                            }
                            [Static Interconnection Networks
                                [LCN
                                    [Hybrid
                                        [Pyramid]
                                        [Diamond]
                                        [MMT]
                                    ]
                                    [4D
                                        [Hypercube]
                                    ]
                                    [3D
                                        [3D Mesh]
                                        [Cube]
                                    ]
                                    [2D
                                        [Ring]
                                        [Mesh]
                                        [2D Torus]
                                        [ILLIAC]
                                        [Fat Tree]
                                        [Tree]
                                    ]
                                    [1D
                                        [Linear Array]
                                    ]
                                ]
                                [CCN
                                    [Completely Connected]
                                ]
                            ]
                        \end{forest}
                    \end{center}

@@

                    \vspace{0.4cm}
                    \noindent
                    \begin{minipage}{0.49\linewidth} % Linear Array
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                        \end{tcolorbox}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                    \vspace{0.3cm}
                    \noindent
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                        \end{tcolorbox}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                    \vspace{0.3cm}
                    \noindent
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                        \end{tcolorbox}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

                    \vspace{0.3cm}
                    \noindent
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

                        \end{tcolorbox}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                    \vspace{0.3cm}
                    \noindent
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

                        \end{tcolorbox}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                    \vspace{0.3cm}
                    \noindent
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                        \end{tcolorbox}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.49\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                    \vspace{0.3cm}
                    \noindent
                    \begin{minipage}{1\linewidth}
                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

>>>>

                        \begin{forest}
                            for tree={rounded corners,
                            draw,
                            text centered,
                            anchor=north,
                            grow=east,
                            anchor=west,
                            parent anchor=east,
                            child anchor=west,
                            l sep=1cm,
                            s sep=0.2cm,
                            tier/.wrap pgfmath arg={level#1}{level()}
                            }
                            [Static Interconnection Networks
                                [LCN
                                    [Hybrid
                                        [Pyramid]
                                        [Diamond]
                                        [MMT]
                                    ]
                                    [4D
                                        [Hypercube]
                                    ]
                                    [3D
                                        [3D Mesh]
                                        [Cube]
                                    ]
                                    [2D
                                        [Ring]
                                        [Mesh]
                                        [2D Torus]
                                        [ILLIAC]
                                        [Fat Tree]
                                        [Tree]
                                    ]
                                    [1D
                                        [Linear Array]
                                    ]
                                ]
                                [CCN
                                    [Completely Connected]
                                ]
                            ]
                        \end{forest}

                    \end{center}

@@

                    \noindent
                    \begin{minipage}{0.4925\linewidth}

                        \vspace{-51pt}

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                            \begin{center}
                                \begin{tikzpicture}

                                    \foreach \i in {1,...,6}
                                        \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n\i) at (\i,0) {};

                                    \foreach \i in {1,...,5}
                                        \draw (n\i) -- (n\the\numexpr\i+1);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % Linear Array

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                            \begin{center}
                                \begin{tikzpicture}

                                    \foreach \x in {1,2,3,4}
                                        \foreach \y in {1,2,3,4}
                                            \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n\x\y) at (\x, \y) {};

                                    \foreach \x in {1,2,3}
                                        \foreach \y in {1,2,3,4}
                                            \draw (n\x\y) -- (n\the\numexpr\x+1 \y);

                                    \foreach \x in {1,2,3,4}
                                        \foreach \y in {1,2,3}
                                            \draw (n\x\y) -- (n\x\the\numexpr\y+1);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % Mesh

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

                            \begin{center}
                                \begin{tikzpicture}

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n1) at (0,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n2) at (2,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n3) at (1,1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n4) at (1,-1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n5) at (0.3,0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n6) at (0.3,-0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n7) at (1.7,0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n8) at (1.7,-0.7) {};

                                    \draw (n1) -- (n5);
                                    \draw (n5) -- (n3);
                                    \draw (n3) -- (n7);
                                    \draw (n7) -- (n2);
                                    \draw (n2) -- (n8);
                                    \draw (n8) -- (n4);
                                    \draw (n4) -- (n6);
                                    \draw (n6) -- (n1);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % Ring

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

                            \begin{center}
                                \begin{tikzpicture}

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n1) at (0,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n2) at (2,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n3) at (1,1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n4) at (1,-1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n5) at (0.3,0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n6) at (0.3,-0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n7) at (1.7,0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n8) at (1.7,-0.7) {};

                                    \draw (n1) -- (n2);
                                    \draw (n1) -- (n3);
                                    \draw (n1) -- (n4);
                                    \draw (n1) -- (n5);
                                    \draw (n1) -- (n6);
                                    \draw (n1) -- (n7);
                                    \draw (n1) -- (n8);
                                    \draw (n2) -- (n3);
                                    \draw (n2) -- (n4);
                                    \draw (n2) -- (n5);
                                    \draw (n2) -- (n6);
                                    \draw (n2) -- (n7);
                                    \draw (n2) -- (n8);
                                    \draw (n3) -- (n4);
                                    \draw (n3) -- (n5);
                                    \draw (n3) -- (n6);
                                    \draw (n3) -- (n7);
                                    \draw (n3) -- (n8);
                                    \draw (n4) -- (n5);
                                    \draw (n4) -- (n6);
                                    \draw (n4) -- (n7);
                                    \draw (n4) -- (n8);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % Completely Connected

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

                            \begin{center}
                                \begin{tikzpicture}

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n1) at (-1,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n2) at (-0.9,0.38) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n3) at (-0.7,0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n4) at (-0.38,0.9) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n5) at (0,1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n6) at (0.38,0.9) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n7) at (0.7,0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n8) at (0.9,0.38) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n9) at (1,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n10) at (0.9,-0.38) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n11) at (0.7,-0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n12) at (0.38,-0.9) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n13) at (0,-1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n14) at (-0.38,-0.9) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n15) at (-0.7,-0.7) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n16) at (-0.9,-0.38) {};

                                    \draw (n1) -- (n2);
                                    \draw (n2) -- (n3);
                                    \draw (n3) -- (n4);
                                    \draw (n4) -- (n5);
                                    \draw (n5) -- (n6);
                                    \draw (n6) -- (n7);
                                    \draw (n7) -- (n8);
                                    \draw (n8) -- (n9);
                                    \draw (n9) -- (n10);
                                    \draw (n10) -- (n11);
                                    \draw (n11) -- (n12);
                                    \draw (n12) -- (n13);
                                    \draw (n13) -- (n14);
                                    \draw (n14) -- (n15);
                                    \draw (n15) -- (n16);
                                    \draw (n16) -- (n1);

                                    \draw (n1) -- (n5);
                                    \draw (n2) -- (n6);
                                    \draw (n3) -- (n7);
                                    \draw (n4) -- (n8);
                                    \draw (n5) -- (n9);
                                    \draw (n6) -- (n10);
                                    \draw (n7) -- (n11);
                                    \draw (n8) -- (n12);
                                    \draw (n9) -- (n13);
                                    \draw (n10) -- (n14);
                                    \draw (n11) -- (n15);
                                    \draw (n12) -- (n16);
                                    \draw (n13) -- (n1);
                                    \draw (n14) -- (n2);
                                    \draw (n15) -- (n3);
                                    \draw (n16) -- (n4);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % ILLIAC

                    \end{minipage}
                    \hfill 
                    \begin{minipage}{0.4925\linewidth}

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                            \begin{center}
                                \begin{tikzpicture}

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (root) at (0,2) {};

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n1) at (-1,1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n2) at (1,1) {};

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n3) at (-1.5,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n4) at (-0.5,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n5) at (0.5,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n6) at (1.5,0) {};

                                    \draw (root) -- (n1);
                                    \draw (root) -- (n2);
                                    \draw (n1) -- (n3);
                                    \draw (n1) -- (n4);
                                    \draw (n2) -- (n5);
                                    \draw (n2) -- (n6);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % Tree

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                            \vspace{-12pt}

                            \begin{center}
                                \begin{tikzpicture}

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n1) at (0,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n2) at (0,1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n3) at (1,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n4) at (1,1) {};

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n5) at (0.3,0.3) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n6) at (0.3,1.3) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n7) at (1.3,0.3) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n8) at (1.3,1.3) {};

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n9) at (2,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n10) at (2,1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n11) at (3,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n12) at (3,1) {};

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n13) at (2.3,0.3) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n14) at (2.3,1.3) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n15) at (3.3,0.3) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n16) at (3.3,1.3) {};

                                    \draw (n1) -- (n2);
                                    \draw (n1) -- (n3);
                                    \draw (n1) -- (n5);
                                    \draw (n2) -- (n4);
                                    \draw (n2) -- (n6);
                                    \draw (n3) -- (n4);
                                    \draw (n3) -- (n7);
                                    \draw (n4) -- (n8);
                                    \draw (n5) -- (n6);
                                    \draw (n5) -- (n7);
                                    \draw (n6) -- (n8);
                                    \draw (n7) -- (n8);

                                    \draw (n9) -- (n10);
                                    \draw (n9) -- (n11);
                                    \draw (n9) -- (n13);
                                    \draw (n10) -- (n12);
                                    \draw (n10) -- (n14);
                                    \draw (n11) -- (n12);
                                    \draw (n11) -- (n15);
                                    \draw (n12) -- (n16);
                                    \draw (n13) -- (n14);
                                    \draw (n13) -- (n15);
                                    \draw (n14) -- (n16);
                                    \draw (n15) -- (n16);

                                    \draw[dashed] (n3) .. controls (1.5,-0.2) .. (n9);
                                    \draw[dashed] (n7) .. controls (1.8,0.1) .. (n13);
                                    \draw[dashed] (n4) .. controls (1.5,1.2) .. (n10);
                                    \draw[dashed] (n8) .. controls (1.8,1.5) .. (n14);

                                    \draw[dashed] (n1) .. controls (1.5,-0.8) .. (n11);
                                    \draw[dashed] (n5) .. controls (1.8,-0.5) .. (n15);
                                    \draw[dashed] (n2) .. controls (1.5,1.8) .. (n12);
                                    \draw[dashed] (n6) .. controls (1.8,2.1) .. (n16);

                                \end{tikzpicture}
                            \end{center}

                            \vspace{-12pt}

                        \end{tcolorbox} % Hypercube

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                            \begin{center}
                                \begin{tikzpicture}

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n1) at (0,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n2) at (0,1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n3) at (1,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n4) at (1,1) {};

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n5) at (0.3,0.3) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n6) at (0.3,1.3) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n7) at (1.3,0.3) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n8) at (1.3,1.3) {};

                                    \draw (n1) -- (n2);
                                    \draw (n1) -- (n3);
                                    \draw (n1) -- (n5);
                                    \draw (n2) -- (n4);
                                    \draw (n2) -- (n6);
                                    \draw (n3) -- (n4);
                                    \draw (n3) -- (n7);
                                    \draw (n4) -- (n8);
                                    \draw (n5) -- (n6);
                                    \draw (n5) -- (n7);
                                    \draw (n6) -- (n8);
                                    \draw (n7) -- (n8);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % Cube

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                            \begin{center}
                                \begin{tikzpicture}

                                    \node[draw, minimum width=3.8cm, minimum height=0.8cm] (LMain1) at (0,4.2) {};

                                    \node[draw, minimum width=0.5cm, minimum height=0.5cm] (L11) at (-1.5,4.2) {};
                                    \node[draw, minimum width=0.5cm, minimum height=0.5cm] (L12) at (-0.5,4.2) {};
                                    \node[draw, minimum width=0.5cm, minimum height=0.5cm] (L13) at (0.5,4.2) {};
                                    \node[draw, minimum width=0.5cm, minimum height=0.5cm] (L14) at (1.5,4.2) {};

                                    \node[draw, minimum width=1.8cm, minimum height=0.8cm] (LMain2) at (1.3,3) {};

                                    \node[draw, minimum width=0.5cm, minimum height=0.5cm] (L21) at (-1.8,3) {};
                                    \node[draw, minimum width=0.5cm, minimum height=0.5cm] (L22) at (-0.8,3) {};

                                    \node[draw, minimum width=1.8cm, minimum height=0.8cm] (LMain3) at (-1.3,3) {};

                                    \node[draw, minimum width=0.5cm, minimum height=0.5cm] (L23) at (0.8,3) {};
                                    \node[draw, minimum width=0.5cm, minimum height=0.5cm] (L24) at (1.8,3) {};

                                    %%%%%%%%%%%%%%%%%%%%%

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n1) at (-3.0,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n2) at (-2.6,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n3) at (-2.2,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n4) at (-1.8,2) {};

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n5) at (-1.4,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n6) at (-1.0,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n7) at (-0.6,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n8) at (-0.2,2) {};

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n9) at (0.2,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n10) at (0.6,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n11) at (1.0,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n12) at (1.4,2) {};

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n13) at (1.8,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n14) at (2.2,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n15) at (2.6,2) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n16) at (3.0,2) {};

                                    %%%%%%%%%%%%%%%%%%%%%

                                    \draw (L11.south) -- (L21.north);
                                    \draw (L11.south) -- (L22.north);

                                    \draw (L13.south) -- (L23.north);
                                    \draw (L13.south) -- (L24.north);

                                    \draw[dashed] (L12.south) -- (L21.north);
                                    \draw[dashed] (L12.south) -- (L22.north);

                                    \draw[dashed] (L14.south) -- (L23.north);
                                    \draw[dashed] (L14.south) -- (L24.north);

                                    %%%%%%%%%%%%%%%%%%%%%%

                                    \draw (L21.south) -- (n1);
                                    \draw (L21.south) -- (n2);
                                    \draw (L21.south) -- (n3);
                                    \draw (L21.south) -- (n4);

                                    \draw (L22.south) -- (n5);
                                    \draw (L22.south) -- (n6);
                                    \draw (L22.south) -- (n7);
                                    \draw (L22.south) -- (n8);

                                    \draw (L23.south) -- (n9);
                                    \draw (L23.south) -- (n10);
                                    \draw (L23.south) -- (n11);
                                    \draw (L23.south) -- (n12);

                                    \draw (L24.south) -- (n13);
                                    \draw (L24.south) -- (n14);
                                    \draw (L24.south) -- (n15);
                                    \draw (L24.south) -- (n16);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % Fat Tree

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                            \begin{center}
                                \begin{tikzpicture}

                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n1) at (0,0) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n2) at (0.15,0.45) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n3) at (0.15,-0.45) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n4) at (0.45,0.8) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n5) at (0.45,-0.8) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n6) at (0.87,1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n7) at (0.87,-1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n8) at (1.32,1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n9) at (1.32,-1) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n10) at (1.74,0.8) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n11) at (1.74,-0.8) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n12) at (2.04,0.45) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n13) at (2.04,-0.45) {};
                                    \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n14) at (2.19,0) {};

                                    \draw (n1) -- (n2);
                                    \draw (n2) -- (n4);
                                    \draw (n4) -- (n6);
                                    \draw (n6) -- (n8);
                                    \draw (n8) -- (n10);
                                    \draw (n10) -- (n12);
                                    \draw (n12) -- (n14);
                                    \draw (n14) -- (n13);
                                    \draw (n13) -- (n11);
                                    \draw (n9) -- (n11);
                                    \draw (n9) -- (n7);
                                    \draw (n5) -- (n7);
                                    \draw (n5) -- (n3);
                                    \draw (n1) -- (n3);

                                    \draw (n1) -- (n11);
                                    \draw (n2) -- (n12);
                                    \draw (n4) -- (n7);
                                    \draw (n10) -- (n9);
                                    \draw (n13) -- (n6);
                                    \draw (n14) -- (n5);
                                    \draw (n3) -- (n8);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % Chordal Ring

                    \end{minipage}

                    \noindent
                    \begin{minipage}{0.4925\linewidth}

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                            \begin{center}
                                \begin{tikzpicture}

                                    \foreach \x in {1,2,3,4}
                                        \foreach \y in {1,2,3,4}
                                            \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n\x\y) at (\x, \y) {};

                                    \foreach \x in {1,2,3}
                                        \foreach \y in {1,2,3,4}
                                            \draw (n\x\y) -- (n\the\numexpr\x+1 \y);

                                    \foreach \x in {1,2,3,4}
                                        \foreach \y in {1,2,3}
                                            \draw (n\x\y) -- (n\x\the\numexpr\y+1);

                                    \draw (n11) .. controls (0.5,0.5) and (0.5,4.5) .. (n14);
                                    \draw (n21) .. controls (1.5,0.5) and (1.5,4.5) .. (n24);
                                    \draw (n31) .. controls (2.5,0.5) and (2.5,4.5) .. (n34);
                                    \draw (n41) .. controls (3.5,0.5) and (3.5,4.5) .. (n44);

                                    \draw (n11) .. controls (0.5,1.5) and (4.5,1.5) .. (n41);
                                    \draw (n12) .. controls (0.5,2.5) and (4.5,2.5) .. (n42);
                                    \draw (n13) .. controls (0.5,3.5) and (4.5,3.5) .. (n43);
                                    \draw (n14) .. controls (0.5,4.5) and (4.5,4.5) .. (n44);

                                \end{tikzpicture}
                            \end{center}

                        \end{tcolorbox} % 2D Torus

                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.4925\linewidth}

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

                            \vspace{-40pt}
                            \begin{center}
                                \begin{tikzpicture}

                                    \foreach \x in {1,2,3,4}
                                        \foreach \y in {1,2,3,4}
                                            \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n\x\y) at (\x, \y) {};

                                    \foreach \x in {1,2,3}
                                        \foreach \y in {1,2,3,4}
                                            \draw (n\x\y) -- (n\the\numexpr\x+1 \y);

                                    \foreach \x in {1,2,3,4}
                                        \foreach \y in {1,2,3}
                                            \draw (n\x\y) -- (n\x\the\numexpr\y+1);

                                    \draw (n11) .. controls (2,0) and (1,5) .. (n24);
                                    \draw (n21) .. controls (3,0) and (2,5) .. (n34);
                                    \draw (n31) .. controls (4,0) and (3,5) .. (n44);
                                    \draw (n41) .. controls (5,2) and (5,6) .. (n14);

                                    \draw (n14) .. controls (0,3) and (5,4) .. (n43);
                                    \draw (n13) .. controls (0,2) and (5,3) .. (n42);
                                    \draw (n12) .. controls (0,1) and (5,2) .. (n41);
                                    \draw (n11) .. controls (0,2) and (0,6) .. (n44);

                                \end{tikzpicture}
                            \end{center}

                            \vspace{-27pt}

                        \end{tcolorbox} % 2D Tour (variation 2)

                    \end{minipage}

                    \vspace{5pt}
                    \noindent
                    \begin{minipage}{1\linewidth}

                        \begin{tcolorbox}[colframe=black!50, colback=white, size=small]

@@

                            \begin{center}
                                \begin{tikzpicture}

                                    \foreach \x in {1,2,3,4}
                                    \foreach \y in {1,2,3,4}
                                        \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n\x\y) at (\x, \y) {};

                                \foreach \x in {1,2,3}
                                    \foreach \y in {1,2,3,4}
                                        \draw (n\x\y) -- (n\the\numexpr\x+1 \y);

                                \foreach \x in {1,2,3,4}
                                    \foreach \y in {1,2,3}
                                        \draw (n\x\y) -- (n\x\the\numexpr\y+1);

                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n211) at (1.4,1.25) {}; 
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n221) at (2.4,1.25) {}; 
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n231) at (3.4,1.25) {}; 
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n241) at (4.4,1.25) {};

                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n212) at (1.4,2.25) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n222) at (2.4,2.25) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n232) at (3.4,2.25) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n242) at (4.4,2.25) {};

                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n223) at (2.4,3.25) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n213) at (1.4,3.25) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n233) at (3.4,3.25) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n243) at (4.4,3.25) {};

                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n214) at (1.4,4.25) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n224) at (2.4,4.25) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n234) at (3.4,4.25) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n244) at (4.4,4.25) {};

                                \draw (n211) -- (n221);
                                \draw (n221) -- (n231);
                                \draw (n231) -- (n241);

                                \draw (n212) -- (n222);
                                \draw (n222) -- (n232);
                                \draw (n232) -- (n242);

                                \draw (n213) -- (n223);
                                \draw (n223) -- (n233);
                                \draw (n233) -- (n243);

                                \draw (n214) -- (n224);
                                \draw (n224) -- (n234);
                                \draw (n234) -- (n244);

                                \draw (n211) -- (n212);
                                \draw (n212) -- (n213);
                                \draw (n213) -- (n214);

                                \draw (n221) -- (n222);
                                \draw (n222) -- (n223);
                                \draw (n223) -- (n224);

                                \draw (n231) -- (n232);
                                \draw (n232) -- (n233);
                                \draw (n233) -- (n234);

                                \draw (n241) -- (n242);
                                \draw (n242) -- (n243);
                                \draw (n243) -- (n244);

                                %%%%%%%%%%%%%%%%%%%%%%%

                                \draw (n11) -- (n211);
                                \draw (n12) -- (n212);
                                \draw (n13) -- (n213);
                                \draw (n14) -- (n214);

                                \draw (n21) -- (n221);
                                \draw (n22) -- (n222);
                                \draw (n23) -- (n223);
                                \draw (n24) -- (n224);

                                \draw (n31) -- (n231);
                                \draw (n32) -- (n232);
                                \draw (n33) -- (n233);
                                \draw (n34) -- (n234);

                                \draw (n41) -- (n241);
                                \draw (n42) -- (n242);
                                \draw (n43) -- (n243);
                                \draw (n44) -- (n244);

                                %%%%%%%%%%%%%%%%%%%%%%%

                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n311) at (1.8,1.5) {}; 
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n321) at (2.8,1.5) {}; 
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n331) at (3.8,1.5) {}; 
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n341) at (4.8,1.5) {};

                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n312) at (1.8,2.5) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n322) at (2.8,2.5) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n332) at (3.8,2.5) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n342) at (4.8,2.5) {};

                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n323) at (2.8,3.5) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n313) at (1.8,3.5) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n333) at (3.8,3.5) {};
                                \node[circle, fill=black, minimum size=5pt, inner sep=0pt] (n343) at (4.8,3.5) {};
